---
title: "Povilo website"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reticulate 

Text in my chapter. More text. Even more text.


```{r, include=FALSE}
library(reticulate)
use_python("/usr/local/bin/python")
```

```{python}
import pandas as pd
d = {"one": [1.0, 2.0, 3.0, 4.0], "two": [4.0, 3.0, 2.0, 1.0]}
dd = pd.DataFrame(d)
dd
```

```{r}
py$dd
```


```{r}
ddd = data.frame(a = 1:3, b=3:5)
ddd
```

```{python}
r.ddd
```


# Dygraphs

```{r}
library(dplyr)
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>%
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```



# KableExtra


```{r}
library(knitr)
library(kableExtra)
library(formattable)
ft_dt <- mtcars[1:5, 1:4]
ft_dt$car <- row.names(ft_dt)
row.names(ft_dt) <- NULL
ft_dt$mpg <- color_tile("white", "orange")(ft_dt$mpg)
ft_dt$cyl <- cell_spec(ft_dt$cyl, angle = (1:5)*60, 
                      background = "red", color = "white", align = "center")
ft_dt$disp <- ifelse(
  ft_dt$disp > 200,
  cell_spec(ft_dt$disp, color = "red", bold = T),
  cell_spec(ft_dt$disp, color = "green", italic = T)
)
ft_dt$hp <- color_bar("lightgreen")(ft_dt$hp)
ft_dt <- ft_dt[c("car", "mpg", "cyl", "disp", "hp")]

kable(ft_dt, escape = F) %>%
  #kable_paper("hover", full_width = F) %>%
  column_spec(5, width = "3cm") %>%
  add_header_above(c(" ", "Hello" = 2, "World" = 2))
```


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
